Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels

### 2017-02-17 PALSE/talk_Kyoto.tex
Replace white-backgroung png of Investissement d'avernir logo with vectorial pdf

\institute[iLM]{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière}
\title[processionary gel]{Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels}
\author[M. Leocmach]{Mathieu Leocmach \hfill{\usebeamerfont{normal text}\texttt{\usebeamercolor[fg]{normal text}\footnotesize @LamSonLeoc\includegraphics[height=1em]{Twitter_Bird}}}\vspace{-\baselineskip}}
\date{%10 August 2016
}
\titlegraphic{\vspace{-\baselineskip}
	\begin{tabu}{X[c]X[c]X[c]X[c]}
		\multicolumn{2}{c}{\usebeamerfont{institute}\usebeamercolor[fg]{institute}ENS de Lyon, Laboratoire de Chimie}&
		\multicolumn{2}{c}{\usebeamerfont{institute}\usebeamercolor[fg]{institute}ENS de Lyon, Laboratoire de Physique}\\\cmidrule(r){1-2}\cmidrule(l){3-4}
		\includegraphics[height=3\baselineskip]{presentation/Hassan}&
		\includegraphics[height=3\baselineskip]{presentation/Cyrille}&
		\includegraphics[height=3\baselineskip]{presentation/Nicolas_Taberlet}&
		\includegraphics[height=3\baselineskip]{../Yaourt/Seb}\\
		Hassan & Cyrille & Nicolas & S\'{e}bastien\\
		Srour & Monnereau & Taberlet & Manneville\\\cmidrule(r){1-2}
		\multicolumn{2}{c}{Martien Duvall Deffo Ayagou}&\\
		\multicolumn{2}{c}{Thi Thanh-Tam Nguyen}&\raisebox{-0.1em}[0pt][0pt]{\includegraphics[height=2\baselineskip]{presentation/invest-avenir.jpg}}&\raisebox{-0.1em}[0pt][0pt]{\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{../Yaourt/NEW-Logo-ERC-OUTLINE}}\\
	\end{tabu}

>>>>

\institute[iLM]{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière}
\title[processionary gel]{Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels}
\author[M. Leocmach]{Mathieu Leocmach \hfill{\usebeamerfont{normal text}\texttt{\usebeamercolor[fg]{normal text}\footnotesize @LamSonLeoc\includegraphics[height=1em]{Twitter_Bird}}}\vspace{-\baselineskip}}
\date{%10 August 2016
}
\titlegraphic{\vspace{-\baselineskip}
	\begin{tabu}{X[c]X[c]X[c]X[c]}
		\multicolumn{2}{c}{\usebeamerfont{institute}\usebeamercolor[fg]{institute}ENS de Lyon, Laboratoire de Chimie}&
		\multicolumn{2}{c}{\usebeamerfont{institute}\usebeamercolor[fg]{institute}ENS de Lyon, Laboratoire de Physique}\\\cmidrule(r){1-2}\cmidrule(l){3-4}
		\includegraphics[height=3\baselineskip]{presentation/Hassan}&
		\includegraphics[height=3\baselineskip]{presentation/Cyrille}&
		\includegraphics[height=3\baselineskip]{presentation/Nicolas_Taberlet}&
		\includegraphics[height=3\baselineskip]{../Yaourt/Seb}\\
		Hassan & Cyrille & Nicolas & S\'{e}bastien\\
		Srour & Monnereau & Taberlet & Manneville\\\cmidrule(r){1-2}
		\multicolumn{2}{c}{Martien Duvall Deffo Ayagou}&\\
		\multicolumn{2}{c}{Thi Thanh-Tam Nguyen}&\raisebox{-0.1em}[0pt][0pt]{\includegraphics[height=2\baselineskip]{presentation/invest-avenir}}&\raisebox{-0.1em}[0pt][0pt]{\includegraphics[height=2\baselineskip,clip=true, trim=6mm 14mm 6mm 0]{../Yaourt/NEW-Logo-ERC-OUTLINE}}\\
	\end{tabu}
